---
title: "Security Culture Diagnostic"
output: 
  powerpoint_presentation:
    reference_doc: template.pptx
params: 
    data: "input2.csv"
---

```{r setup, include=FALSE}
library(extrafont)
extrafont::font_import(pattern = 'Roboto', prompt=FALSE)
extrafont::loadfonts(device="pdf")
extrafont::loadfonts(device="postscript")
library(gridExtra)
library(tufte)
library(ggradar)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(plyr)
library(cowplot)
library(jsonlite)
suppressPackageStartupMessages(library(dplyr))
library(scales)
library(tibble)
library(stringr)
library(likert)
library(RColorBrewer)

knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
```

### Security Culture Overview

This is an R Markdown presentation. Markdown is a simple formatting 
syntax for authoring HTML, PDF, and MS Word documents. For more 
details on using R Markdown see [Lance Hayden's Work](http://rmarkdown.rstudio.com).

When you click the **Knit** button a document will be generated that 
includes both content as well as the output of any embedded R code 
chunks within the document.

### Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

### Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```
### Slide with Plot

```{r fig-secculture, fig.cap = "Security Culture Survey Results", fig.fullwidth=TRUE, cache = FALSE, message=FALSE, echo=FALSE, results='hide'}
calculate_control <- function(C) {
  culture = as.character(C[1])
  if (isTRUE(all.equal(culture,"Compliance"))) {
    return ("Tight")
  } else if (isTRUE(all.equal(culture, "Process"))) {
    return ("Tight")
  } else if (isTRUE(all.equal(culture, "Autonomy"))) {
    return ("Loose")
  } else if (isTRUE(all.equal(culture, "Trust"))) {
    return ("Loose")
  }
  return ("ERROR")
}

calculate_orientation <- function(C) {
  culture = as.character(C[1])
  if (isTRUE(all.equal(culture, "Compliance"))) {
    return ("External")
  } else if (isTRUE(all.equal(culture, "Process"))) {
    return ("Internal")
  } else if (isTRUE(all.equal(culture,"Autonomy"))) {
    return ("External")
  } else if (isTRUE(all.equal(culture, "Trust"))) {
    return ("Internal")
  }
  return ("ERROR")
} 
scds = read.csv(file=params$data)
# reshape the data from wide to long, combining the A/B/C/D columns
# https://clayford.github.io/dwir/dwr_05_combine_merge_rehsape_data.html
better = melt(scds, id.vars = c("question", "respondent"), measure.vars = c("Compliance","Autonomy","Trust","Process"))



# calculate the mean of the responses for each question
# http://www.cookbook-r.com/Manipulating_data/Summarizing_data/#using-ddply
cdata = ddply(better, 
              c("question", "variable"), 
              summarize, 
              mean = mean(value), 
              control = calculate_control(variable),
              orientation = calculate_orientation(variable)
              )

cdata$orientation2 <- factor(cdata$orientation, levels=rev(levels(factor(cdata$orientation))))
cdata$control2 <- factor(cdata$control, levels=rev(levels(factor(cdata$control))))

p = ggplot(cdata, aes(x=factor(question, levels=c(10:1)), y=mean) ) +
  geom_bar(stat='identity') + 
  scale_y_continuous(limits = c(0,10), labels = c("0", "2.5", "5", "7.5", "10")) +
  scale_x_discrete(labels=c("1" = "Org Values", "2" = "Org Behaves",
                            "3" = "Definition", "4" = "Information",
                            "5" = "Operations", "6" = "Technology",
                            "7" = "People", "8" = "Risk",
                            "9" = "Accountability", "10" = "Performance")) +
  coord_flip() + 
  labs(x="", y="") + 
  theme_few() +
  theme(text = element_text(size=5), legend.position="none", panel.grid.minor = element_line()) +
  annotate("text", x=8.5,y=7.5,label=c("Process","Compliance","Trust","Autonomy"), size=1.75) +
  facet_grid( control2 ~ orientation2 )
#ggdraw(p)

ggdraw(add_sub(p, "Security Culture diagnostic created by Lance Hayden, PhD (CC BY-SA 4.0)", x = 0, hjust = 0, size=4))
```